---
title: "p8150_h1_sc4935"
author: "Shiwei Chen"
date: "9/25/2021"
output: github_document
---

```{r}
library(tidyverse)
```



# Problem 1

### Firstly, we create a data frame include 4 different type variables.

```{r}
problem1_df = 
  tibble(
    norm_samp = rnorm(10),
    ele_great_0 = norm_samp > 0,
    animal = c("Rhinos", "Kittens", "Raccoons", "Goats", "Skunks", "Hedgehogs", "Otters", "Giraffes", "Seals", "Fox"),
    animal_type = factor(c("herbivore", "carnivores", "omnivorous",  "herbivore", "omnivorous", "omnivorous", "carnivores", "herbivore", "carnivores", "omnivorous"))
    )

problem1_df
```

### Secondly, we take the mean of each variable in the dataframe.

```{r}
mean(pull(problem1_df, norm_samp))
mean(pull(problem1_df, ele_great_0))
mean(pull(problem1_df, animal))
mean(pull(problem1_df, animal_type))
```



### Third, we convert variables from one type to another.

```{r, echo=FALSE}
as.numeric(pull(problem1_df, ele_great_0))
as.numeric(pull(problem1_df, animal))
as.numeric(pull(problem1_df, animal_type))
```


We pull the data we required from the data frame, then we use the as.numeric function to convert variables from one type to another.

In conclusion, since the true or false and the levels of characters can be easily formatted numbers, the logic variables(ele_great_0) are converted to 0 and 1, and the factor variables(animal_type) are converted to 1,2 and 3. But, the strings of the character variables are not properly formatted numbers, so, when we run the character variables, it cannot be converted to the numeric class, and only shows NAs.





# Problem 2






