---
title: "p8150_hw1_sc4935"
author: "Shiwei Chen"
date: "9/25/2021"
output: github_document
---

```{r, message=FALSE}
library(tidyverse)
```



# Problem 1

### Firstly, we create a data frame include 4 different type variables.

```{r}
problem1_df = 
  tibble(
    norm_samp = rnorm(10),
    ele_great_0 = norm_samp > 0,
    animal = c("Rhinos", "Kittens", "Raccoons", "Goats", "Skunks", "Hedgehogs", "Otters", "Giraffes", "Seals", "Fox"),
    animal_type = factor(c("herbivore", "carnivores", "omnivorous",  "herbivore", "omnivorous", "omnivorous", "carnivores", "herbivore", "carnivores", "omnivorous"))
    )

problem1_df
```



### Secondly, we take the mean of each variable in the dataframe.

```{r, warning=FALSE}
mean(pull(problem1_df, norm_samp))
mean(pull(problem1_df, ele_great_0))
mean(pull(problem1_df, animal))
mean(pull(problem1_df, animal_type))
```

So, the mean of norm_samp is around -0.43, the mean of ele_great_0 is 0.5, but the mean of animal and animal_type are both NAs.



### Third, we convert variables from one type to another.

```{r, results='hide', warning=FALSE}
as.numeric(pull(problem1_df, ele_great_0))
as.numeric(pull(problem1_df, animal))
as.numeric(pull(problem1_df, animal_type))
```

We pull the data we required from the data frame, then we use the as.numeric function to convert variables from one type to another.

In conclusion, since the true or false and the levels of characters can be easily formatted numbers, the logic variables(ele_great_0) are converted to 0 and 1, and the factor variables(animal_type) are converted to 1,2 and 3. But, the strings of the character variables are not properly formatted numbers, so, when we run the character variables, it cannot be converted to the numeric class, and only shows NAs.





# Problem 2

## Palmer Penguins Project

```{r}
data("penguins", package = "palmerpenguins")
```



### First describe the data in dataset, including the names/values of important variables.

```{r}
names(penguins)
skimr::skim(penguins)
```



### Describe the size of data set.

```{r}
nrow(penguins)
ncol(penguins)
```
So, there are 344 rows and 8 colums within the dataset.



### Calculate the mean flipper length.

```{r}
mean(penguins$flipper_length_mm, na.rm = TRUE)
```
So, the mean of flipper length is around 201.



### Scatter Plot

```{r, warning=FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("penguins_scatter_plot.pdf", height = 6, width = 4)
```